Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS

### 2022-04-21 R/CONUS_AOD.Rmd
switch CONUS report to pdf

---
title: "Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS"
output: html_document
bibliography: references.json
---

@@

```{r basics, echo=FALSE}
library(targets)
library(data.table)
library(DT)
library(patchwork)
library(ggplot2)
library(sf)
library(knitr)
```

@@

```{r table_cv_results, echo=FALSE}
tar_load(cv_summary_tables)
DT::datatable(cv_summary_tables$stat,
              rownames = FALSE,
              fillContainer = FALSE,
              autoHideNavigation = TRUE,
              options = list(pageLength = 50,
                             autoWidth = TRUE))
```

@@

@@

```{r strata_year, echo=FALSE, eval=TRUE}
dtwrapper(dt[, performance_aod(.SD), keyby = year(aer_date)])
```

@@

```{r strata_month, echo=FALSE}
dtwrapper(dt[, performance_aod(.SD), keyby = month(aer_date)])
```

@@

```{r strata_qa, echo=FALSE}
dtwrapper(dt[, performance_aod(.SD), by = qa_best])
```

@@

```{r strata_water, echo=FALSE}
dtwrapper(dt[, performance_aod(.SD), by = qa_lwsi])
```

@@

```{r strata_overpasses, echo=FALSE}
dt[, overpasses := .N, by = c("Site_Name", "aer_date")]
dtwrapper(dt[, performance_aod(.SD), keyby = overpasses])
```

@@

```{r strata_noaa_regions, echo=FALSE}
# performance by NOAA climate regions
dtwrapper(dt[, performance_aod(.SD), keyby = state.noaa.region])

@@

```{r agreement_plot, warning=FALSE, echo=FALSE}
p1 <- ggplot(dt[AOD_470nm < 1 & MCD19_AOD_470nm < 1]) +
  aes(AOD_470nm, MCD19_AOD_470nm) +
  geom_abline(linetype = "dashed") +
  geom_point(alpha = 0.01) +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs")) +
  scale_x_continuous("AERONET AOD 470nm", limits = c(0, 1)) +
  scale_y_continuous("MAIAC AOD 470nm", limits = c(0, 1)) +
  theme_bw() +
  theme(aspect.ratio = 1) + 
  labs(caption = paste0("Not shown: ", dt[AOD_470nm > 1 | MCD19_AOD_470nm > 1, .N], " AOD values outside [0, 1]"))

@@

@@

```{r shap_rank, echo=FALSE}
# what do the SHAPs tell us?
tar_load(initial_cv_l2_terra_conus)
shaps <- initial_cv_l2_terra_conus$"shap_score"
# sort by importance
kable(sort(sapply(abs(shaps), mean), decreasing = TRUE), 
      format = "html",
      table.attr = "style='width:30%;'",
      digits = 3, col.names = "Mean Abs SHAP")
```

>>>>

---
title: "Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS"
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}  #make every figure with caption = h, this was the fix
output: pdf_document
always_allow_html: true
bibliography: references.json
---

@@

```{r basics, echo=FALSE}
library(targets)
library(data.table)
library(DT)
library(patchwork)
library(ggplot2)
library(sf)
library(knitr)
library(kableExtra)
# library(flextable)
# set_flextable_defaults(fonts_ignore=TRUE)
```

@@

```{r table_cv_results, echo=FALSE}
tar_load(cv_summary_tables)
result <- (cv_summary_tables$stat)
kbl(result, col.names = gsub(pattern = "\\.|_", " ", names(result))) %>% 
  kable_styling(latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1cm")
```

@@

*still to be added*

@@

```{r strata_year, echo=FALSE, eval=TRUE}
result <- dt[, performance_aod(.SD), keyby = year(aer_date)]
kbl(result, col.names = gsub(pattern = "\\.|_", " ", names(result))) %>% 
  kable_styling(latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1cm")
```

@@

```{r strata_month, echo=FALSE}
result <- dt[, performance_aod(.SD), keyby = month(aer_date)]
kbl(result, col.names = gsub(pattern = "\\.|_", " ", names(result))) %>% 
  kable_styling(latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1cm")
```

@@

```{r strata_qa, echo=FALSE}
result <- dt[, performance_aod(.SD), by = qa_best]
kbl(result, col.names = gsub(pattern = "\\.|_", " ", names(result))) %>% 
  kable_styling(latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1cm")
```

@@

```{r strata_water, echo=FALSE, fig.pos="H"}
result <- dt[, performance_aod(.SD), by = qa_lwsi]
kbl(result, col.names = gsub(pattern = "\\.|_", " ", names(result))) %>% 
  kable_styling(latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1cm")
```

@@

```{r strata_overpasses, echo=FALSE, fig.pos="H"}
dt[, overpasses := .N, by = c("Site_Name", "aer_date")]
result <- dt[, performance_aod(.SD), keyby = overpasses]
kbl(result, col.names = gsub(pattern = "\\.|_", " ", names(result))) %>% 
  kable_styling(latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1cm")

@@

```{r strata_noaa_regions, echo=FALSE, fig.pos="H"}
# performance by NOAA climate regions
result <- dt[, performance_aod(.SD), keyby = state.noaa.region]
kbl(result, col.names = gsub(pattern = "\\.|_", " ", names(result))) %>% 
  kable_styling(latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1cm")

@@

```{r agreement_plot, echo=FALSE, dev='png', dpi=300}
p1 <- ggplot(dt[AOD_470nm < 1 & MCD19_AOD_470nm < 1]) +
  aes(AOD_470nm, MCD19_AOD_470nm) +
  geom_abline(linetype = "dashed") +
  geom_point(alpha = 0.01) +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs")) +
  scale_x_continuous("AERONET AOD 470nm", limits = c(0, 1)) +
  scale_y_continuous("MAIAC AOD 470nm", limits = c(0, 1)) +
  theme_bw() +
  theme(aspect.ratio = 1) + 
  labs(caption = paste0("Not shown: ", dt[AOD_470nm > 1 | MCD19_AOD_470nm > 1, .N], " AOD values outside [0, 1]"))

@@

------------------------------------------------------------------------

@@

```{r shap_rank, echo=FALSE}
# what do the SHAPs tell us?
tar_load(initial_cv_l2_terra_conus)
shaps <- initial_cv_l2_terra_conus$"shap_score"
# sort by importance
df_shap <- data.frame(meanabsshap = round(sort(sapply(abs(shaps), mean), decreasing = TRUE), 4))
kbl(df_shap, col.names = "Mean |SHAP|")
# df_shap$variable <- row.names(df_shap)
# ft_shap <- flextable(df_shap[, c(2, 1)])
# ft_shap <- set_header_labels(ft_shap, list(variable = "Variable", meanabsshap = "Mean Absolute SHAP"))
# ft_shap
```
